%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Site Reliability Engineer} % Job title
    {Shopee Singapore} % Organization
    {Singapore} % Location
    {May 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project driver for an internal platform used for incident alerting and resolution, written in Golang with Gin framework.}
        \begin{itemize}
          \item{Equivalent to doing development, product and project management.}
        \end{itemize}
        \item {Independently delivered backend features for internal platforms through design, planning, implementation, testing, maintenance.}
        \item {Contributed to the development, maintenance and support of several internal platforms including resource capacity planner, autoscaler, stress tester, disaster recovery controller.}
        \item {Weekly rotational on duty support for users of our platforms.}
        \item {Dedicated SRE assigned to multiple dev teams, in charge of investigating and solving various issues reported by devs.}
        \item {Monthly campaign preparation and midnight standby for traffic spikes.}
        \item {Conducted technical interviews for recruitment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer Intern} % Job title
    {Zendesk Singapore} % Organization
    {Singapore} % Location
    {Jan 2020 - Jul 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bash scripted a packaging workflow as part of the plan to autoscale edge region EC2 servers.}
        \item {Implemented a Slack bot that gathers relevant information for finding out what happened during an incident.}
        \item {Rolling restarted production servers as part of security patching exercise.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer Intern} % Job title
    {UX Consulting} % Organization
    {Singapore} % Location
    {Oct 2016 - Feb 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Experimented with MEAN (Mongo, Express, Angular, Node) stack to implement a prototype internal website for calendar booking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
