%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {https://nuswhispers.fyi/} % Role
    {NUSWhispers Analysis} % Project Name
    {Singapore} % Location
    {Jan 2020 - Jan 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Hackathon project which I polished to completion.}
        \item {Daily scraping of NUSWhispers facebook posts for fresh data.}
        \item {Analyzed posts data with pandas for stats, sklearn TF-IDF for topic modeling, and post network analysis.}
        \item {Developed responsive web frontend with React and Tailwind.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {https://russiaslosses.netlify.app/} % Role
    {Russia's Losses} % Project Name
    {Singapore} % Location
    {Mar 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {1 week project to visualize Russia's military lossses over time in the Ukraine war.}
        \item {Daily scraping of KyivIndependent's "Russia's losses" images and text extraction using Tesseract.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Guy} % Role
    {LisTent - Short-form Audio Social Media App} % Project Name
    {Singapore} % Location
    {Oct 2020 - Nov 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Final Project for CS3216 (Software Product Engineering) where teams of 4 students work like a startup.}
        \item {Setup infrastructure on AWS EC2, S3, MongoDB Atlas.}
        \item {Setup continuous deployment using Github Actions and Ansible with multistage environments.}
        \item {Assisted in creating marketing assets to advertise the app.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Role
    {Nyx - Artificial Intelligence} % Project Name
    {Singapore} % Location
    {Apr 2016 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Final Year Project which won SiTF and Microsoft Imagine Cup awards.}
        \item {Designed and developed a web chat UI, taking inspiration from Telegram and WhatsApp Web.}
        \item {Researched and integrated Firebase realtime database for the chat UI.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
